---
  title: "DESeq Analysis"
author: "Britney & Luoyu"
date: "4/11/2021"
output:
  html_document:
  df_print: paged
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DESeq2)
```

## Import Data
```{r}
setwd("/Users/zhangluoyu/Desktop/DGE_celegans/htseqdata")
#countdatas, set working directory first to read the tabular file
count_data = read.table("Galaxy327.tabular")
colnames(count_data) = c("Gene","0_R1-0_S1","0_R1-8_S13","0_R2-0_S4","0_R2-8_S16","0_R3-0_S7","0_R3-8_S19","0_R4-0_S10","0_R4-8_S22","10_R1-0_S2","10_R1-8_S14","10_R2-0_S5","10_R2-8_S17","10_R3-0_S8","10_R3-8_S20","10_R4-0_S11","10_R4-8_S23","100_R1-0_S3","100_R1-8_S15","100_R2-0_S6","100_R2-8_S18","100_R3-0_S9","100_R3-8_S21","100_R4-0_S12","100_R4-8_S24")
countdata = count_data[,-1]
rownames(countdata) = count_data[,1]
#count_data = count_data %>% remove_rownames %>% column_to_rownames(var="Gene")



#all data on the 0 days
countdata_0days_0_10<-subset(countdata, select = c("0_R1-0_S1","0_R2-0_S4","0_R3-0_S7","0_R4-0_S10","10_R1-0_S2","10_R2-0_S5", "10_R3-0_S8","10_R4-0_S11"))
countdata_0days_0_100<-subset(countdata, select = c("0_R1-0_S1","0_R2-0_S4","0_R3-0_S7","0_R4-0_S10","100_R1-0_S3","100_R2-0_S6","100_R3-0_S9","100_R4-0_S12"))
countdata_0days_10_100<-subset(countdata, select = c("10_R1-0_S2","10_R2-0_S5", "10_R3-0_S8","10_R4-0_S11","100_R1-0_S3","100_R2-0_S6","100_R3-0_S9","100_R4-0_S12"))
#all data on the 8 days
countdata_8days_0_10<-subset(countdata, select = c("0_R1-8_S13","0_R2-8_S16","0_R3-8_S19","0_R4-8_S22","10_R1-8_S14","10_R2-8_S17","10_R3-8_S20","10_R4-8_S23"))
countdata_8days_0_100<-subset(countdata, select = c("0_R1-8_S13","0_R2-8_S16","0_R3-8_S19","0_R4-8_S22","100_R1-8_S15","100_R2-8_S18","100_R3-8_S21","100_R4-8_S24"))
countdata_8days_10_100<-subset(countdata, select = c("10_R1-8_S14","10_R2-8_S17","10_R3-8_S20","10_R4-8_S23","100_R1-8_S15","100_R2-8_S18","100_R3-8_S21","100_R4-8_S24"))
#all data on the 0 conc
countdata_0conc<-subset(countdata, select = c("0_R1-0_S1","0_R1-8_S13","0_R2-0_S4","0_R2-8_S16","0_R3-0_S7","0_R3-8_S19","0_R4-0_S10","0_R4-8_S22"))
#all data on the 10 conc
countdata_10conc<-subset(countdata, select = c("10_R1-0_S2","10_R1-8_S14","10_R2-0_S5","10_R2-8_S17","10_R3-0_S8","10_R3-8_S20","10_R4-0_S11","10_R4-8_S23"))
#all data on the 100 conc
countdata_100conc<-subset(countdata, select = c("100_R1-0_S3","100_R1-8_S15","100_R2-0_S6","100_R2-8_S18","100_R3-0_S9","100_R3-8_S21","100_R4-0_S12","100_R4-8_S24"))


#metadatas for corresponding countdatas                                               
meta_data = read.csv("Metadata_b.csv", header = TRUE)
meta_data$conc = as.factor(meta_data$conc)
meta_data$rap = as.factor(meta_data$rap)
meta_data$day = as.factor(meta_data$day)

meta_data_0days_0_10<- subset(meta_data, (day == 0 & (conc == 0 | conc ==10)))
meta_data_0days_0_100<- subset(meta_data, (day == 0 & (conc == 0 | conc ==100)))
meta_data_0days_10_100<- subset(meta_data, (day == 0 & (conc == 10 | conc ==100)))
meta_data_8days_0_10<- subset(meta_data, (day == 8 & (conc == 0 | conc ==10)))
meta_data_8days_0_100<- subset(meta_data, (day == 8 & (conc == 0 | conc ==100)))
meta_data_8days_10_100<- subset(meta_data, (day == 8 & (conc == 10 | conc ==100)))
meta_data_0conc<- subset(meta_data, conc == 0)
meta_data_10conc<- subset(meta_data, conc == 10)
meta_data_100conc<- subset(meta_data, conc == 100)


#dds files for each group: 0/8 days to compare conc effect; 0/10/100 conc to compare days effect
dds_0days_0_10 = DESeqDataSetFromMatrix(countData = countdata_0days_0_10,
                                        colData = meta_data_0days_0_10,
                                        design = ~ conc)
dds_0days_0_100 = DESeqDataSetFromMatrix(countData = countdata_0days_0_100,
                                         colData = meta_data_0days_0_100,
                                         design = ~ conc)
dds_0days_10_100 = DESeqDataSetFromMatrix(countData = countdata_0days_10_100,
                                          colData = meta_data_0days_10_100,
                                          design = ~ conc)
dds_8days_0_10 = DESeqDataSetFromMatrix(countData = countdata_8days_0_10,
                                        colData = meta_data_8days_0_10,
                                        design = ~ conc)
dds_8days_0_100 = DESeqDataSetFromMatrix(countData = countdata_8days_0_100,
                                         colData = meta_data_8days_0_100,
                                         design = ~ conc)
dds_8days_10_100 = DESeqDataSetFromMatrix(countData = countdata_8days_10_100,
                                          colData = meta_data_8days_10_100,
                                          design = ~ conc)
dds_0conc = DESeqDataSetFromMatrix(countData = countdata_0conc,
                                   colData = meta_data_0conc,
                                   design = ~ day)
dds_10conc = DESeqDataSetFromMatrix(countData = countdata_10conc,
                                    colData = meta_data_10conc,
                                    design = ~ day)
dds_100conc = DESeqDataSetFromMatrix(countData = countdata_100conc,
                                     colData = meta_data_100conc,
                                     design = ~ day)

dds_0days_0_10 = DESeq(dds_0days_0_10)
dds_0days_0_100 = DESeq(dds_0days_0_100)
dds_0days_10_100 = DESeq(dds_0days_10_100)
dds_8days_0_10 = DESeq(dds_8days_0_10)
dds_8days_0_100 = DESeq(dds_8days_0_100)
dds_8days_10_100 = DESeq(dds_8days_10_100)
dds_0conc = DESeq(dds_0conc)
dds_10conc = DESeq(dds_10conc)
dds_100conc = DESeq(dds_100conc)
```


## Results Table
```{r}
res_0days_0_10 = results(dds_0days_0_10)
head(results(dds_0days_0_10, tidy=TRUE))

res_0days_0_100 = results(dds_0days_0_100)
head(results(dds_0days_0_100, tidy=TRUE))

res_0days_10_100 = results(dds_0days_10_100)
head(results(dds_0days_10_100, tidy=TRUE))

res_8days_0_10 = results(dds_8days_0_10)
head(results(dds_8days_0_10, tidy=TRUE))

res_8days_0_100 = results(dds_8days_0_100)
head(results(dds_8days_0_100, tidy=TRUE))

res_8days_10_100 = results(dds_8days_10_100)
head(results(dds_8days_10_100, tidy=TRUE))

res_0conc = results(dds_0conc)
head(results(dds_0conc, tidy=TRUE))

res_10conc = results(dds_10conc)
head(results(dds_10conc, tidy=TRUE))

res_100conc = results(dds_100conc)
head(results(dds_100conc, tidy=TRUE))
```


## Summary of differential gene expression & Sorting by adjusted p-value
```{r}

summary(res_0days_0_10)
res_0days_0_10 = res_0days_0_10[order(res_0days_0_10$padj),]
head(res_0days_0_10)

summary(res_0days_0_100)
res_0days_0_100 = res_0days_0_100[order(res_0days_0_100$padj),]
head(res_0days_0_100)

summary(res_0days_10_100)
res_0days_10_100 = res_0days_10_100[order(res_0days_10_100$padj),]
head(res_0days_10_100)

summary(res_8days_0_10)
res_8days_0_10 = res_8days_0_10[order(res_8days_0_10$padj),]
head(res_8days_0_10)

summary(res_8days_0_100)
res_8days_0_100 = res_8days_0_100[order(res_8days_0_100$padj),]
head(res_8days_0_100)

summary(res_8days_10_100)
res_8days_10_100 = res_8days_10_100[order(res_8days_10_100$padj),]
head(res_8days_10_100)

summary(res_0conc)
res_0conc = res_0conc[order(res_0conc$padj),]
head(res_0conc)

summary(res_10conc)
res_10conc = res_10conc[order(res_10conc$padj),]
head(res_10conc)

summary(res_100conc)
res_100conc = res_100conc[order(res_100conc$padj),]
head(res_100conc)
```


## plotCounts
```{r}
#e.g. compare the normalized counts between different LC concentrations for the top 6 genes
par(mfrow=c(2,3))
plotCounts(dds, gene="WBGene00004978", intgroup="conc")
plotCounts(dds, gene="WBGene00019380", intgroup="conc")
plotCounts(dds, gene="WBGene00014165", intgroup="conc")
plotCounts(dds, gene="WBGene00018891", intgroup="conc")
plotCounts(dds, gene="WBGene00021585", intgroup="conc")
plotCounts(dds, gene="WBGene00015525", intgroup="conc")
```


## Volcano Plot
#0days
#0_10
par(mfrow=c(1,1))
#basic plot
with(res_0days_0_10, plot(log2FoldChange, -log10(pvalue), pch = 20, panel.first=grid(), main = "Volcano plot", xlim=c(-3,3)))
#colored points: blue if padj < 0.01, red if log2FC > 1 and padj < 0.05)
with(subset(res_0days_0_10, padj < .01 ), points(log2FoldChange, -log10(pvalue), pch = 20, col="blue"))
with(subset(res_0days_0_10, padj < .05 & abs(log2FoldChange) > 1), points(log2FoldChange, -log10(pvalue), pch = 20, col = "red"))

#cut off line
abline(v=0)
abline(v=c(-1,1), col="brown")
abline(h=-log10(0.05), col="brown")

#showing gene
gn.selected = abs(res_0days_0_10$log2FoldChange) > 1 & res_0days_0_10$padj < 0.05
text(res_0days_0_10$log2FoldChange[gn.selected],
     -log10(res_0days_0_10$padj)[gn.selected],
     lab=rownames(res_0days_0_10)[gn.selected ], cex=0.5)
gn.selected_up = res_0days_0_10$log2FoldChange > 1 & res_0days_0_10$padj < 0.05
gn.selected_down = res_0days_0_10$log2FoldChange < -1 & res_0days_0_10$padj < 0.05
david0days_0_10_up<-data.frame(rownames(res_0days_0_10)[gn.selected_up ])
david0days_0_10_down<-data.frame(rownames(res_0days_0_10)[gn.selected_down ])
write.csv(na.omit(david0days_0_10_up),"~/Desktop/DGE_celegans/updown/0days_0_10_up.csv", row.names = FALSE)
write.csv(na.omit(david0days_0_10_down),"~/Desktop/DGE_celegans/updown/0days_0_10_down.csv", row.names = FALSE)

#0_100
par(mfrow=c(1,1))
#basic plot
with(res_0days_0_100, plot(log2FoldChange, -log10(pvalue), pch = 20, panel.first=grid(), main = "Volcano plot", xlim=c(-3,3)))
#colored points: blue if padj < 0.01, red if log2FC > 1 and padj < 0.05)
with(subset(res_0days_0_100, padj < .01 ), points(log2FoldChange, -log10(pvalue), pch = 20, col="blue"))
with(subset(res_0days_0_100, padj < .05 & abs(log2FoldChange) > 1), points(log2FoldChange, -log10(pvalue), pch = 20, col = "red"))

#cut off line
abline(v=0)
abline(v=c(-1,1), col="brown")
abline(h=-log10(0.05), col="brown")

#showing gene
gn.selected = abs(res_0days_0_100$log2FoldChange) > 1 & res_0days_0_100$padj < 0.05 
text(res_0days_0_100$log2FoldChange[gn.selected],
     -log10(res_0days_0_100$padj)[gn.selected],
     lab=rownames(res_0days_0_100)[gn.selected ], cex=0.5)
david0days_0_100<-data.frame(rownames(res_0days_0_100)[gn.selected ])
gn.selected_up = res_0days_0_100$log2FoldChange > 1 & res_0days_0_100$padj < 0.05
gn.selected_down = res_0days_0_100$log2FoldChange < -1 & res_0days_0_100$padj < 0.05
david0days_0_100_up<-data.frame(rownames(res_0days_0_100)[gn.selected_up ])
david0days_0_100_down<-data.frame(rownames(res_0days_0_100)[gn.selected_down ])
write.csv(na.omit(david0days_0_100_up),"~/Desktop/DGE_celegans/updown/0days_0_100_up.csv", row.names = FALSE)
write.csv(na.omit(david0days_0_100_down),"~/Desktop/DGE_celegans/updown/0days_0_100_down.csv", row.names = FALSE)

#10_100
par(mfrow=c(1,1))
#basic plot
with(res_0days_10_100, plot(log2FoldChange, -log10(pvalue), pch = 20, panel.first=grid(), main = "Volcano plot", xlim=c(-3,3)))
#colored points: blue if padj < 0.01, red if log2FC > 1 and padj < 0.05)
with(subset(res_0days_10_100, padj < .01 ), points(log2FoldChange, -log10(pvalue), pch = 20, col="blue"))
with(subset(res_0days_10_100, padj < .05 & abs(log2FoldChange) > 1), points(log2FoldChange, -log10(pvalue), pch = 20, col = "red"))

#cut off line
abline(v=0)
abline(v=c(-1,1), col="brown")
abline(h=-log10(0.05), col="brown")

#showing gene
gn.selected = abs(res_0days_10_100$log2FoldChange) > 1 & res_0days_10_100$padj < 0.05 
text(res_0days_10_100$log2FoldChange[gn.selected],
     -log10(res_0days_10_100$padj)[gn.selected],
     lab=rownames(res_0days_10_100)[gn.selected ], cex=0.5)
david0days_10_100<-data.frame(rownames(res_0days_10_100)[gn.selected ])
gn.selected_up = res_0days_10_100$log2FoldChange > 1 & res_0days_10_100$padj < 0.05
gn.selected_down = res_0days_10_100$log2FoldChange < -1 & res_0days_10_100$padj < 0.05
david0days_10_100_up<-data.frame(rownames(res_0days_10_100)[gn.selected_up ])
david0days_10_100_down<-data.frame(rownames(res_0days_10_100)[gn.selected_down ]) 
write.csv(na.omit(david0days_10_100_up),"~/Desktop/DGE_celegans/updown/0days_10_100_up.csv", row.names = FALSE)
write.csv(na.omit(david0days_10_100_down),"~/Desktop/DGE_celegans/updown/0days_10_100_down.csv", row.names = FALSE)

#8days
#0_10
par(mfrow=c(1,1))
#basic plot
with(res_8days_0_10, plot(log2FoldChange, -log10(pvalue), pch = 20, panel.first=grid(), main = "Volcano plot", xlim=c(-3,3)))
#colored points: blue if padj < 0.01, red if log2FC > 1 and padj < 0.05)
with(subset(res_8days_0_10, padj < .01 ), points(log2FoldChange, -log10(pvalue), pch = 20, col="blue"))
with(subset(res_8days_0_10, padj < .05 & abs(log2FoldChange) > 1), points(log2FoldChange, -log10(pvalue), pch = 20, col = "red"))

#cut off line
abline(v=0)
abline(v=c(-1,1), col="brown")
abline(h=-log10(0.05), col="brown")

#showing gene
gn.selected = abs(res_8days_0_10$log2FoldChange) > 1 & res_8days_0_10$padj < 0.05 
text(res_8days_0_10$log2FoldChange[gn.selected],
     -log10(res_8days_0_10$padj)[gn.selected],
     lab=rownames(res_8days_0_10)[gn.selected ], cex=0.5)
david8days_0_10<-data.frame(rownames(res_8days_0_10)[gn.selected ])
gn.selected_up = res_8days_0_10$log2FoldChange > 1 & res_8days_0_10$padj < 0.05
gn.selected_down = res_8days_0_10$log2FoldChange < -1 & res_8days_0_10$padj < 0.05
david8days_0_10_up<-data.frame(rownames(res_8days_0_10)[gn.selected_up ])
david8days_0_10_down<-data.frame(rownames(res_8days_0_10)[gn.selected_down ])
write.csv(na.omit(david8days_0_10_up),"~/Desktop/DGE_celegans/updown/8days_0_10_up.csv", row.names = FALSE)
write.csv(na.omit(david8days_0_10_down),"~/Desktop/DGE_celegans/updown/8days_0_10_down.csv", row.names = FALSE)

#0_100
par(mfrow=c(1,1))
#basic plot
with(res_8days_0_100, plot(log2FoldChange, -log10(pvalue), pch = 20, panel.first=grid(), main = "Volcano plot", xlim=c(-3,3)))
#colored points: blue if padj < 0.01, red if log2FC > 1 and padj < 0.05)
with(subset(res_8days_0_100, padj < .01 ), points(log2FoldChange, -log10(pvalue), pch = 20, col="blue"))
with(subset(res_8days_0_100, padj < .05 & abs(log2FoldChange) > 1), points(log2FoldChange, -log10(pvalue), pch = 20, col = "red"))

#cut off line
abline(v=0)
abline(v=c(-1,1), col="brown")
abline(h=-log10(0.05), col="brown")

#showing gene
gn.selected = abs(res_8days_0_100$log2FoldChange) > 1 & res_8days_0_100$padj < 0.05 
text(res_8days_0_100$log2FoldChange[gn.selected],
     -log10(res_8days_0_100$padj)[gn.selected],
     lab=rownames(res_8days_0_100)[gn.selected ], cex=0.5)
david8days_0_100<-data.frame(rownames(res_8days_0_100)[gn.selected ])
gn.selected_up = res_8days_0_100$log2FoldChange > 1 & res_8days_0_100$padj < 0.05
gn.selected_down = res_8days_0_100$log2FoldChange < -1 & res_8days_0_100$padj < 0.05
david8days_0_100_up<-data.frame(rownames(res_8days_0_100)[gn.selected_up ])
david8days_0_100_down<-data.frame(rownames(res_8days_0_100)[gn.selected_down ])
write.csv(na.omit(david8days_0_100_up),"~/Desktop/DGE_celegans/updown/8days_0_100_up.csv", row.names = FALSE)
write.csv(na.omit(david8days_0_100_down),"~/Desktop/DGE_celegans/updown/8days_0_100_down.csv", row.names = FALSE)


#10_100
par(mfrow=c(1,1))
#basic plot
with(res_8days_10_100, plot(log2FoldChange, -log10(pvalue), pch = 20, panel.first=grid(), main = "Volcano plot", xlim=c(-3,3)))
#colored points: blue if padj < 0.01, red if log2FC > 1 and padj < 0.05)
with(subset(res_8days_10_100, padj < .01 ), points(log2FoldChange, -log10(pvalue), pch = 20, col="blue"))
with(subset(res_8days_10_100, padj < .05 & abs(log2FoldChange) > 1), points(log2FoldChange, -log10(pvalue), pch = 20, col = "red"))

#cut off line
abline(v=0)
abline(v=c(-1,1), col="brown")
abline(h=-log10(0.05), col="brown")

#showing gene
gn.selected = abs(res_8days_10_100$log2FoldChange) > 1 & res_8days_10_100$padj < 0.05 
text(res_8days_10_100$log2FoldChange[gn.selected],
     -log10(res_8days_10_100$padj)[gn.selected],
     lab=rownames(res_8days_10_100)[gn.selected ], cex=0.5)
david8days_10_100<-data.frame(rownames(res_8days_10_100)[gn.selected ])
gn.selected_up = res_8days_10_100$log2FoldChange > 1 & res_8days_10_100$padj < 0.05
gn.selected_down = res_8days_10_100$log2FoldChange < -1 & res_8days_10_100$padj < 0.05
david8days_10_100_up<-data.frame(rownames(res_8days_10_100)[gn.selected_up ])
david8days_10_100_down<-data.frame(rownames(res_8days_10_100)[gn.selected_down ])
write.csv(na.omit(david8days_10_100_up),"~/Desktop/DGE_celegans/updown/8days_10_100_up.csv", row.names = FALSE)
write.csv(na.omit(david8days_10_100_down),"~/Desktop/DGE_celegans/updown/8days_10_100_down.csv", row.names = FALSE)


#0conc
par(mfrow=c(1,1))
#basic plot
with(res_0conc, plot(log2FoldChange, -log10(pvalue), pch = 20, panel.first=grid(), main = "Volcano plot", xlim=c(-3,3)))
#colored points: blue if padj < 0.01, red if log2FC > 1 and padj < 0.05)
with(subset(res_0conc, padj < .01 ), points(log2FoldChange, -log10(pvalue), pch = 20, col="blue"))
with(subset(res_0conc, padj < .05 & abs(log2FoldChange) > 1), points(log2FoldChange, -log10(pvalue), pch = 20, col = "red"))

#cut off line
abline(v=0)
abline(v=c(-1,1), col="brown")
abline(h=-log10(0.05), col="brown")

#showing gene
gn.selected = abs(res_0conc$log2FoldChange) > 1 & res_0conc$padj < 0.05 
text(res_0conc$log2FoldChange[gn.selected],
     -log10(res_0conc$padj)[gn.selected],
     lab=rownames(res_0conc)[gn.selected ], cex=0.5)
gn.selected_up = res_0conc$log2FoldChange > 1 & res_0conc$padj < 0.05 
gn.selected_down = res_0conc$log2FoldChange < -1 & res_0conc$padj < 0.05
david0conc_up<-data.frame(rownames(res_0conc)[gn.selected_up ])
david0conc_down<-data.frame(rownames(res_0conc)[gn.selected_down ])
write.csv(na.omit(david0conc_up),"~/Desktop/DGE_celegans/updown/0conc_up.csv", row.names = FALSE)
write.csv(na.omit(david0conc_down),"~/Desktop/DGE_celegans/updown/0conc_down.csv", row.names = FALSE)


#10conc
par(mfrow=c(1,1))
#basic plot
with(res_10conc, plot(log2FoldChange, -log10(pvalue), pch = 20, panel.first=grid(), main = "Volcano plot", xlim=c(-3,3)))
#colored points: blue if padj < 0.01, red if log2FC > 1 and padj < 0.05)
with(subset(res_10conc, padj < .01 ), points(log2FoldChange, -log10(pvalue), pch = 20, col="blue"))
with(subset(res_10conc, padj < .05 & abs(log2FoldChange) > 2), points(log2FoldChange, -log10(pvalue), pch = 20, col = "red"))

#cut off line
abline(v=0)
abline(v=c(-1,1), col="brown")
abline(h=-log10(0.05), col="brown")

#showing gene
gn.selected = abs(res_10conc$log2FoldChange) > 1 & res_10conc$padj < 0.05 
text(res_10conc$log2FoldChange[gn.selected],
     -log10(res_10conc$padj)[gn.selected],
     lab=rownames(res_10conc)[gn.selected ], cex=0.5)
gn.selected_up = res_10conc$log2FoldChange > 1 & res_10conc$padj < 0.05 
gn.selected_down = res_10conc$log2FoldChange < -1 & res_10conc$padj < 0.05
david10conc_up<-data.frame(rownames(res_10conc)[gn.selected_up ])
david10conc_down<-data.frame(rownames(res_10conc)[gn.selected_down ])
write.csv(na.omit(david10conc_up),"~/Desktop/DGE_celegans/updown/10conc_up.csv", row.names = FALSE)
write.csv(na.omit(david10conc_down),"~/Desktop/DGE_celegans/updown/10conc_down.csv", row.names = FALSE)


#100conc
par(mfrow=c(1,1))
#basic plot
with(res_100conc, plot(log2FoldChange, -log10(pvalue), pch = 20, panel.first=grid(), main = "Volcano plot", xlim=c(-3,3)))
#colored points: blue if padj < 0.01, red if log2FC > 1 and padj < 0.05)
with(subset(res_100conc, padj < .01 ), points(log2FoldChange, -log10(pvalue), pch = 20, col="blue"))
with(subset(res_100conc, padj < .025 & abs(log2FoldChange) > 1), points(log2FoldChange, -log10(pvalue), pch = 20, col = "red"))

#cut off line
abline(v=0)
abline(v=c(-1,1), col="brown")
abline(h=-log10(0.05), col="brown")

#showing gene
gn.selected = abs(res_100conc$log2FoldChange) > 1 & res_100conc$padj < 0.025 
text(res_100conc$log2FoldChange[gn.selected],
     -log10(res_100conc$padj)[gn.selected],
     lab=rownames(res_100conc)[gn.selected ], cex=0.5)
gn.selected_up = res_100conc$log2FoldChange > 1 & res_100conc$padj < 0.05 
gn.selected_down = res_100conc$log2FoldChange < -1 & res_100conc$padj < 0.05
david100conc_up<-na.omit(data.frame(rownames(res_100conc)[gn.selected_up ]))
david100conc_down<-data.frame(rownames(res_100conc)[gn.selected_down ])
write.csv(na.omit(david100conc_up),"~/Desktop/DGE_celegans/updown/100conc_up.csv", row.names = FALSE)
write.csv(na.omit(david100conc_down),"~/Desktop/DGE_celegans/updown/100conc_down.csv", row.names = FALSE)


## PCA
```{r}
vsdata = vst(dds, blind=FALSE)
plotPCA(vsdata, intgroup="conc")

vsdata_0days_0_10 = vst(dds_0days_0_10, blind=FALSE)
plotPCA(vsdata_0days_0_10, intgroup="conc")
text(x=1,labels=seq_along(meta_data_0days_0_10$rap))


vsdata_0days_0_100 = vst(dds_0days_0_100, blind=FALSE)
plotPCA(vsdata_0days_0_100, intgroup="conc")

vsdata_0days_10_100 = vst(dds_0days_10_100, blind=FALSE)
plotPCA(vsdata_0days_10_100, intgroup="conc")


vsdata_8days_0_10 = vst(dds_8days_0_10, blind=FALSE)
plotPCA(vsdata_8days_0_10, intgroup="conc")

vsdata_8days_0_100 = vst(dds_8days_0_100, blind=FALSE)
plotPCA(vsdata_8days_0_100, intgroup="conc")

vsdata_8days_10_100 = vst(dds_8days_10_100, blind=FALSE)
plotPCA(vsdata_8days_10_100, intgroup="conc")

vsdata_0conc = vst(dds_0conc, blind=FALSE)
plotPCA(vsdata_0conc, intgroup="day")

vsdata_10conc = vst(dds_10conc, blind=FALSE)
plotPCA(vsdata_10conc, intgroup="day")

vsdata_100conc = vst(dds_100conc, blind=FALSE)
plotPCA(vsdata_100conc, intgroup="day")
```
